\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Chapter_4}
\author{44-274-Md. Zobayer Hasan Nayem}
\date{July 2022}

\begin{document}


\section{Implementation}
\text{We developed a software that why people are easily using his payment system. They can easily deposit his money, transfer his money, also he can buy Crypto-currency, he can easily exchange BDT to USD. he can check daily Crypto-currency Rate.We have also developed a E-mail Verification System, That's why a user can any transaction safely. It's a OTP Verification System.}

\section{Software Tools}
\subsection{Xampp}
\text{XAMPP is a cross-platform web server that is free and open-source. XAMPP is a short form for Cross-Platform, Apache, MySQL, PHP, and Perl. XAMPP is a popular cross-platform web server that allows programmers to write and test their code on a local webserver. It was created by Apache Friends, and the public can revise or modify its native source code. It includes MariaDB, Apache HTTP Server, and interpreters for PHP and Perl, among other computer languages. Because of XAMPP’s simplicity of deployment, a developer can quickly
and easily install a WAMP or LAMP stack on an operating system, with the added benefit that common add-in apps like WordPress and Joomla can also be loaded.}

\subsection{Visual Studio Community}
\text{Visual Studio is an Integrated Development Environment (IDE) developed by Microsoft to develop GUI (Graphical User Interface), console, Web applications, web apps, mobile apps, cloud, and web services, etc. With the help of this IDE, you can create managed code as well as native code. It uses the various platforms of Microsoft software development software like Windows store, Microsoft Silverlight, and Windows API, etc. It is not a language-specific
IDE as you can use this to write code in C#, C++, VB(Visual Basic), Python, JavaScript, and many more languages. It provides support for 36 different programming languages. It is available for Windows as well as for macOS.}


\end{document}